3D MAGNETIC MODELLING FOR ELIPSOIDS

### 2016-11-29 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Atualizacao da introducao

In the 19th century \cite{dirichlet1839nouvelle}, manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals.

In the late 19th century \cite{maxwell1881treatise}, showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field. He also presented the formulae of the demagnetizing field in a uniformly magnetized ellipsoid of revolution.

\cite{osborn1945demagnetizing}, published formulas for the demagnetizing factors of the general ellipsoid alongside with a table of values for different proportions of semi-axis

\cite{stoner1945xcvii}, presented a more simple and friendly formulae of the demagnetizing factors for an ellipsoid, with step-by-step deduction. This work includes formulae for different parametrizations for the ellipsoid (triaxial, prolate, oblate).

\cite{peake1953magnetic} published the formulas for the external field of ellipsoid of revolution in terms of elliptical integrals for external fields.

\cite{chang1961fields} published the formulas for the external field of triaxial, prolate and oblate ellipsoids in terms of elliptical integrals for external fields.

In the decade of 1970 \cite{farrar1979some} showed in his work the value of the elipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia. The elipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.

The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes. Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model. This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
A generalized model for triaxials ellipsoids was published by \cite{clark1986magnetic}. Both in Emerson et al. and Clark et al. works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the position $(0,0,0)$ in the center of the ellipsoid (through a matrix of rotation). However, the codes presented for HP-41C are outdated and doesn't have a detailed descrition of the algorithm.

\cite{tejedor1995external}, presented a work where they calculate the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.

\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources. A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.

\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.

>>>>

In the 19th century, \cite{dirichlet1839nouvelle} manage to solve the problem of the potential of a homogeneous ellipsoid with semi-axes $a \ge b \ge c$ by using the first and second Legendre's normal elliptic integrals. Later, \cite{maxwell1881treatise} showed that only bodies of second degree can be uniformly magnetized when placed in a uniform field. He also presented the formulae of the demagnetizing field in a uniformly magnetized ellipsoid of revolution.

The formulas for the demagnetizing factors of the general ellipsoid alongside a table of values for different proportions of semi-axis was published by \cite{osborn1945demagnetizing}. In the same year, \cite{stoner1945xcvii} presented a more simple and friendly formulas of the demagnetizing factors for an ellipsoid, with step-by-step deduction. This work includes formulas for different parametrizations for the ellipsoid (triaxial, prolate, oblate).

A decade later, \cite{peake1953magnetic} published a paper with the formulas for the external field of ellipsoid of revolution. Some years after that, \cite{chang1961fields} showed the formulas for the external field of triaxial, prolate and oblate ellipsoids. Both used the Dirichlet solution in terms of elliptical integrals for external fields.
More recently, \cite{tejedor1995external}, gave the calculations of the external field generated by ellipsoids using a variational method, in contrast to the usual method of Dirichlet.

In the decade of 1970 \cite{farrar1979some} showed in his work the value of the ellipsoidal model in geophysic exploration, where it was used for analysis of magnetic anomalies in Tennant Creeks's gold mine in Australia. The ellipsoid was the most correct geometry to model bodies of lenticular pipe shape and the most appropriate to handle self-desmagnetization of bodies of high susceptibilty - magnetic susceptibility higher than 0.1 SI \citep{clark2014methods}.
\cite{guo1998self}, showed three case studies of the importance of self-demagnetization of high susceptibilties bodies when modelling magnetic sources. A magnetic-iron deposit, volcanic-hosted iron deposit and an ultramafic-hoste nickel andcopper deposits.
The same author years later,\cite{guo2001systematic}, published another paper analysing the errors of what an uncorrected by demagnetization data can affect on anmalies interpretation.

The magnetic field resultant of an ellipsoid was presented the first time in full modeling in the space domain by \cite{emerson1985magnetic}, along a compilation of several others geometric shapes. Through a consistent notation this work tapped a hole in the literature that missed the ellipsoidal model. This model, however, consists in a division between prolate and oblate ellipsoids, with a few differences in the algorithm.
A generalized model for triaxials ellipsoids was published by \cite{clark1986magnetic}. Both in Emerson et al. and Clark et al. works, they were the firsts to include the calculations of the magnetic field in a different coordinate system other than with the position $(0,0,0)$ in the center of the ellipsoid (through a matrix of rotation). However, the codes presented for HP-41C are outdated and doesn't have a descrition of the algorithm, difficulting the reproduction by the cientific commnunity. This may the reason why the magnetic field modelling of the ellipsoid, in general, is only used through comercial softwares.
